### 2025-09-15 paper/sec/evaluation.tex
[update] remove toprule

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{p{3cm} p{6cm} p{4cm}}
        \toprule
        \textbf{Ambiguity Type} & \textbf{Example} & \textbf{Explanation} \\
        \midrule

@@

        \midrule
        missing-data &
        The average methane emissions for the year 2015 is \hl{1.0} &
        November is missing to calculate the average correctly. \\

        \midrule
        false statement &
        We additionally make comparisons with stacked CNNs and hierarchical attention (Vaswani et al., 2017), shown in Table 3 (the CNN and Transformer rows), BiLSTM is \hl{the most efficient} among all models compared, with the highest model size &
        BiLSTM is not the most efficient, nor does it have the largest size. \\

        \midrule
        incorrect numerical value &
        LSTM is the fastest model with overall time taken being \hl{90} seconds &
        It is not 90 but 106. \\

        \midrule
        ambiguous referent &
        LSTM is the fastest model with overall time taken being \hl{90} seconds &
        There are two type of time in the dataset (training\_time, execution\_time), both with a value of 90 seconds. \\

        \bottomrule
    \end{tabular}
    \caption{Negative cases example without the \emph{Data} column.}
    \label{tab:ambiguita}
\end{table}

>>>>

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{p{3cm} p{6cm} p{4cm}}
        \hline
        \textbf{Ambiguity Type} & \textbf{Example} & \textbf{Explanation} \\
        \hline

@@

        missing-data &
        The average methane emissions for the year 2015 is \hl{1.0} &
        November is missing to calculate the average correctly. \\

        false statement &
        We additionally make comparisons with stacked CNNs and hierarchical attention (Vaswani et al., 2017), shown in Table 3 (the CNN and Transformer rows), BiLSTM is \hl{the most efficient} among all models compared, with the highest model size &
        BiLSTM is not the most efficient, nor does it have the largest size. \\

        incorrect numerical value &
        LSTM is the fastest model with overall time taken being \hl{90} seconds &
        It is not 90 but 106. \\

        ambiguous referent &
        LSTM is the fastest model with overall time taken being \hl{90} seconds &
        There are two type of time in the dataset (training\_time, execution\_time), both with a value of 90 seconds. \\

        \hline
    \end{tabular}
    \caption{Negative cases example without the \emph{Data} column.}
    \label{tab:ambiguita}
\end{table}
